The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
add laforge

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure 1,
@Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO: something broken here?? -->
Further, for social interactions or associations to occur individuals must share
space, and thus have overlapping home ranges. In the context of the social
environment, home range overlap is a relatively coarse scale of sociality across
which individuals share space over larger spatial and temporal scales [e.g.
@Piza_Roca_2018]. <!-- what is going on here -->Although the social environment clearly scales spatially and
temporally, it remains unclear whether coarser scales of sociality, including
social association and home range overlap, vary predictably with social
interaction [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the
type of social relationship observed that can be explicitly defined and measured
[@Farine_2015a]. <!-- Farine references comes out as D.R. Farine 2015 -->

>>>>

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure 1,
@Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO: something broken here?? -->
Further, for social interactions or associations to occur individuals must share
space, and thus have overlapping home ranges [@Laforge_2014]. In the context of the social
environment, home range overlap is a relatively coarse scale of sociality across
which individuals share space over larger spatial and temporal scales [e.g.
@Piza_Roca_2018]. <!-- double coarse -->Although the social environment clearly scales spatially and
temporally, it remains unclear whether coarser scales of sociality, including
social association and home range overlap, vary predictably with social
interaction [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the
type of social relationship observed that can be explicitly defined and measured
[@Farine_2015a]. <!-- Farine references comes out as D.R. Farine 2015 -->
